### 2023-04-10 main/chapter_theory.tex
begin waffle on c1n2; clarify covariant derivatives

\paragraph{Weyl-Dirac.}
The Weyl-Dirac summand $\mathcal{L}_\mathrm{WD}$ implements the fermions and
their gauge interactions, and can be written:
\begin{equation}
\begin{split}
\mathcal{L}_\mathrm{WD} =
\sum_i^3
\Bigl(
& L^\dagger_i \sigma^\mu \mathcal{D}_\mu L_i
+ \bar e^\dagger_i \sigma^\mu \mathcal{D}_\mu \bar e_i \\
& + \mathbf{Q}^\dagger_i \sigma^\mu \mathcal{D}_\mu \mathbf{Q}_i
+ \mathbf{\bar u}^\dagger_i \sigma^\mu \mathcal{D}_\mu \mathbf{\bar u}_i
+ \mathbf{\bar d}^\dagger_i \sigma^\mu \mathcal{D}_\mu \mathbf{\bar d}_i
\Bigr)
,
\end{split}
\end{equation}
where the $\mathcal{D}_\mu$ expressions corresponding to the fermion fields:
$L_i$ for lepton doublets,
$\bar e_i$ for lepton singlets,
$\mathbf{Q}_i$ for quark doublets,
and $\mathbf{\bar u}_i$ and $\mathbf{\bar d}_i$ for up- and down-type quark
singlets, respectively.
The notation $\bar x$ indicates the Dirac adjoint of $x$.
The three fermion generations are indexed by $i$.
The quark fields are in colour triplets.

@@

\paragraph{Higgs.}
Finally, the Higgs term,
\begin{equation}
\mathcal{L}_\mathrm{Higgs} =
(\mathcal{D}_\mu H)^\dagger (\mathcal{D}^\mu H)
- \left[ -\mu^2 H^\dagger H + \lambda (H^\dagger H)^2 \right]
,
\end{equation}
contains the dynamics and potential for the scalar Higgs doublet.
The symbol $\mathcal{D}_\mu$ is a gauge-covariant derivative operator.
The notation $x^\dagger$ indicates the hermitian conjugate of $x$.
The potential terms are isolated into square brackets to highlight the negative
sign on the mass term $\mu^2$, which with the quartic term contributes to
spontaneous symmetry breaking~\cite{rubakov1999classical}.

@@

A convenient first decomposition of the MSSM Lagrangian's parts splits it into
four parts:
\begin{equation}
\mathcal{L}_\mathrm{MSSM} =
\mathcal{L}_\mathrm{SUSY}
+ \mathcal{L}_\mathrm{soft}
+ \mathcal{L}_\mathrm{gf}
+ \mathcal{L}_\mathrm{ghost}
,
\end{equation}
in which
$\mathcal{L}_\mathrm{SUSY}$ is the supersymmetric part,
$\mathcal{L}_\mathrm{soft}$ is the a `softly' breaking part
(which is necessary because supersymmetry is not an unbroken symmetry of
nature),
and
$\mathcal{L}_\mathrm{gf}$ and $\mathcal{L}_\mathrm{ghost}$
are two additions that are necessary for quantization of the
theory~\cite{kuroda1999complete}.

@@

\paragraph{Others.}
The gauge-fixing term $\mathcal{L}_\mathrm{gf}$ ensures that the gauge boson
propagators take the Standard Model form.
The ghost term $\mathcal{L}_\mathrm{ghost}$ introduces special scalar fields
that interact with bosons in the theory, but which have no effect at tree-level
but are necessary for self-consistency of the theory in loop diagrams.

\subsection{Specific simplified models}
\TODO{C1N2 and GMSB for $\twoljets$}

>>>>

\paragraph{Weyl-Dirac.}
The Weyl-Dirac summand $\mathcal{L}_\mathrm{WD}$ implements the fermions and
their gauge interactions, and can be written:
\begin{equation}
\begin{split}
\mathcal{L}_\mathrm{WD} =
\sum_i^3
\Bigl(
& L^\dagger_i \sigma^\mu \mathcal{D}_\mu L_i
+ \bar e^\dagger_i \sigma^\mu \mathcal{D}_\mu \bar e_i \\
& + \mathbf{Q}^\dagger_i \sigma^\mu \mathcal{D}_\mu \mathbf{Q}_i
+ \mathbf{\bar u}^\dagger_i \sigma^\mu \mathcal{D}_\mu \mathbf{\bar u}_i
+ \mathbf{\bar d}^\dagger_i \sigma^\mu \mathcal{D}_\mu \mathbf{\bar d}_i
\Bigr)
,
\end{split}
\end{equation}
where each of the the $\mathcal{D}_\mu$ operators expresses a unique covariant
derivative that corresponds to the operand field.
These fermion fields are labelled
$L_i$ for lepton doublets,
$\bar e_i$ for lepton singlets,
$\mathbf{Q}_i$ for quark doublets,
and $\mathbf{\bar u}_i$ and $\mathbf{\bar d}_i$ for up- and down-type quark
singlets, respectively.
The notation $\bar x$ indicates the Dirac adjoint of $x$.
The three fermion generations are indexed by $i$.
The quark fields are in colour triplets.

@@

\paragraph{Higgs.}
Finally, the Higgs term,
\begin{equation}
\mathcal{L}_\mathrm{Higgs} =
(\mathcal{D}_\mu H)^\dagger (\mathcal{D}^\mu H)
- \left[ -\mu^2 H^\dagger H + \lambda (H^\dagger H)^2 \right]
,
\end{equation}
contains the dynamics and potential for the scalar Higgs doublet.
The symbol $\mathcal{D}_\mu$ is a gauge-covariant derivative operator
specific to the Higgs field.
The notation $x^\dagger$ indicates the hermitian conjugate of $x$.
The potential terms are isolated into square brackets to highlight the negative
sign on the mass term $\mu^2$, which with the quartic term contributes to
spontaneous symmetry breaking~\cite{rubakov1999classical}.

@@

A convenient first decomposition of the MSSM Lagrangian's parts splits it into
four parts:
\begin{equation}
\mathcal{L}_\mathrm{MSSM} =
\mathcal{L}_\mathrm{SUSY}
+ \mathcal{L}_\mathrm{soft}
+ \mathcal{L}_\mathrm{GF}
+ \mathcal{L}_\mathrm{ghost}
,
\end{equation}
in which
$\mathcal{L}_\mathrm{SUSY}$ is the supersymmetric part,
$\mathcal{L}_\mathrm{soft}$ is the a `softly' breaking part
(which is necessary because supersymmetry is not an unbroken symmetry of
nature),
and
$\mathcal{L}_\mathrm{GF}$ and $\mathcal{L}_\mathrm{ghost}$
are two additions that are necessary for quantization of the
theory~\cite{kuroda1999complete}.

@@

\paragraph{Others.}
The gauge-fixing term $\mathcal{L}_\mathrm{GF}$ ensures that the gauge boson
propagators take the Standard Model form.
The ghost term $\mathcal{L}_\mathrm{ghost}$ introduces special scalar fields
that interact with bosons in the theory, but which have no effect at tree-level
but are necessary for self-consistency of the theory in loop
diagrams~\cite{martin2016primer, kuroda1999complete}.

\subsection{Specific simplified models}
Two specific simplified supersymmetric models are studied in this thesis.
These models were selected for the \atlas\ `$\twoljets$'
search~\cite{atlas2022searches},
presented in Chapter~\ref{chapter:2ljets},
because they are well-studied but not-yet excluded models that can affect the
data in its targetted signature of data with two charged leptons,
hadronic jets, and missing transverse momentum.
Within the context of $\twoljets$, we name these two simplified models
`C1N2' and `GMSB'.
\TODO{add citations}

\paragraph{C1N2.}
`C1N2' is a restricted subset of the MSSM in which the only active SUSY
particles
are the lightest chargino ($\chargino_1$)
and the lightest two neutralinos ($\neutralino_1$, $\neutralino_2$).
The name `C1N2` is an abbreviation to
`Chargino 1' concatenated with `Neutralino 2'.

\paragraph{GMSB.}
`GMSB' is \TODO{}.
